Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-15 journal-draft/bare_jrnl_comsoc.tex
Di's answers to Erwin's initial modidication in the section of system model

In addition to the licensed channels there is one dedicated control channel. It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase. $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$. 
Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., . \textcolor{red}{(The rendez-vous should be briefly explained! TODO)} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.

@@

\textcolor{red}{As to a pair of secondary users, when the distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other. DEFINE DISTANCE! TODO for Di!}

If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.	
%
%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
%While primary users are assumed to be fixed, secondary users can be mobile.
%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)} of connectivity is solely based on the distance between secondary users,
%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
%Due to relatively low primary user dynamics, time index is omitted here.
%%In order to perform clustering, CR users first need to establish their neighborhood.
%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.

A cognitive readio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$. Note that we consider the channel availability only for \textit{one} snapshot of time. For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.

@@

A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member. Further it also notifies the members to use a different common control channel for payload communication. (\textcolor{red}{(Not clear what the meaning of payload communication is. Why not omitting payload here?)}

>>>>

In addition to the licensed channels there is one dedicated control channel. It is available for any secondary node $n$ to exchange control messages with any other node in its proximity (or neighborhood) $N(n)$ during the cluster formation phase. $N(n)$ is simply defined as the set of nodes located within the transmission range of $n$. 
%To establish the communications with neighbours, 
Control messages involved in the clustering process can be transmitted on available licensed channels through a rendezvous process by channel hopping~\cite{channelHopping_Rendezvous_2014, Gu_distributed_rendezvous_2014}, i.e., two neighbouring nodes establish communication on the same channel. \textcolor{brown}{rendezvous, done} Over the control channel, a secondary user $n$ can exchange its spectrum sensing result $C_n$ to any $n' \in N(n)$.

@@

As to a pair of secondary users, when the Euclidean distance between them is smaller than secondary users' transmission range, we assume the pair is able to communicate on both control channel and licensed channel, and the both are considered to be neighbours of each other. DEFINE DISTANCE! \textcolor{brown}{distance, done}
%
If a secondary user $n$ is not in the transmission range of a primary user $u$, $n$ can certainly not detect the presence of $u$.
As the transmission range of primary users is limited and secondary users are located at different locations, different secondary users may have different views of the spectrum availability, i.e., for any $n, n' \in \mathcal{N}$, $C_n = C_{n'}$ does not necessarily hold.	
%
%Neighbourhood establishment and maintenance with control channel and according to a neighborhood discovery protocol which is out of scope of our work.
%While primary users are assumed to be fixed, secondary users can be mobile.
%Validation refers to the process of ensuring that no primary transmission is actually taking place on the respective channel.
%All $N$ secondary users constitute an ad-hoc network in which data can be transmitted from one certain node to any other node should available c.hannels are available on the source node, destination node and other intermediate nodes.
%Communication on licensed channels is possible only when nodes $i, j$ are both located in each other's transmission range and both share a validated licensed channel.
As the assumed $0/1$ state \textcolor{red}{(What is that?? Define! Fix it TODO)}\textcolor{brown}{Di: 0/1 means the connectivity is either available or not} of connectivity is solely based on the Euclidean distance between secondary users,
%CRN can be represented by a graph $\mathcal{G}(I,\mathcal{E})$, where $\mathcal{E}=\lbrace(i,j,v) \vert i, j \in \mathcal{N} \wedge v\in V_i \wedge v\in V_j \rbrace$ is wireless link between any secondary node $i$ and its neighbour $j$ with licensed channel $v$.
%Due to relatively low primary user dynamics, time index is omitted here.
%%In order to perform clustering, CR users first need to establish their neighborhood.
%For secondary node $i$, its neighborhood $Nb_i$ consists of all the secondary users locating within its transmission range, regardless whether common licensed channels exist or not. 
%% and have at least one common channel with node $i$ each, i.e. $ j\in Nb_i \Rightarrow V_i\cap V_j\neq \emptyset$.
%%The clustering phase is initialized during which any control message is again conveyed by the control channel.
%In the rest of this paper, \textit{channel} only refers to the licensed common control channel unless the dedicated control channel is particularly mentioned.

A cognitive radio network (CRN) can be represented as an undirected graph $G = (\mathcal{N}, E)$, where $E \subseteq \mathcal{N} \times \mathcal{N}$ such that $\{n_1,n_2\} \in E$  if, and only if, there exists a channel $c \in \mathcal{C}$ with $c \in C_{n_1} \cap C_{n_2}$. Note that we consider the channel availability only for \textit{one} snapshot of time. For the rest of this paper the word channel is referred to licensed channel, if the control channel is not explicitly mentioned.

@@

A cluster head coordinates the activities of cluster members, \ie it notifies all the members to vacate a channel if a primary user's presence is detected by one cluster member. Further it also notifies the members to use a different common control channel for payload communication. (\textcolor{red}{(Not clear what the meaning of payload communication is. Why not omitting payload here?)} \textcolor{brown}{payload communication happens when the clusters are formed, and start to support network functionalities, e.g. routing. Thus I think it is necessary to leave it here.}
